---
title: "Markdown and Leaflet"
author: "IsaacVillatoro"
date: "September 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extreme poverty in Guatemala

This project is done with the purpose of showing the knowledge acquired during the second week of the course. To carry out the project it is necessary to use R Markdown and Leaflet.

The goal is to create a web page that displays a custom map using the Javascript Leaflet library.

The map is created based on the index of extreme poverty in Guatemala, according to the data provided by the National Institute of Statistics of Guatemala.

The poverty mapping methodology allows the estimation of poverty and inequality indicators, to a greater level of geographical disaggregation than that traditionally allows a household survey. To estimate a poverty map, it is necessary to have information on a monetary measure of welfare (consumption or income) of households and to have a large enough number of households to produce reliable estimates.

### Data

I Create a CSV file only with Guatemala departments, including poverty indices. Each department will have its latitude and longitude.

The data base is in https://www.ine.gob.gt/index.php/estadisticas-continuas/mapas-de-pobreza

```{r}
# Data in my wd
gt_cities <- read.csv("gt_data.csv")

print(gt_cities)
```

### Map

Finally using the leaflet library created in Javascript was made the map, so that the density circles were of a suitable size multiplied the index by 700.

```{r}
library(leaflet)
gt_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = gt_cities$pop*700)
```


*Source: Encovi 2011 and Rural Poverty Maps 2011.*

*Notes. - Only rural areas. The total poverty rate was calculated using the official line of Qz.8282.9. The extreme poverty rate was calculated using the official line of Qz.4380.*